---
title: "Summary Report"
---

```{r}
#| include: false
targets::tar_source('R')
```

## Data Summary

For this project, we are using three datasets. The first dataset includes Adelie adult and chick counts across islands and years.

```{r}
#| echo: true
#| eval: true
#| warning: false
#| label: chicks-summary

tar_load(full_datasets)

datasummary_skim(data = full_datasets$counts %>% select(c(island, adults, chicks)))
```


----


The second dataset describes the monthly weather conditions from Palmer Station, Antarctica

```{r}
#| echo: true
#| eval: true
#| warning: false
#| label: weather-summary

tar_load(weather_raw) 

datasummary_skim(data = weather_raw %>% clean_names())

```


---


The final dataset is a widely accessible dataset through the `palmerpenguins` package and includes many variables concerning penguin body condition.

```{r}
#| echo: true
#| eval: true
#| warning: false
#| label: penguins-summary

datasummary_skim(data = full_datasets$penguins %>% select(-c(month, date, comments, clutch_completion, species, study_name)))

```

## Modelling

We had two groups of models. The first was looking at how temperature relates to chick counts on different islands.

```{r}
#| echo: true
#| eval: true
#| label: counts-models

tar_load(model_tables)

model_tables

```

------------------------------------------------------------------------

The second was looking at how precipitation affects body mass of Adelie penguins.

```{r}
#| echo: true
#| eval: true
#| label: penguins-models

tar_load(model_penguins_groups)
tar_load(penguin_keys)

model_penguins_groups %>% setNames(penguin_keys) %>% modelsummary()

```

## Plots

We can visualize these models. Chick counts:

```{r}
#| echo: true
#| eval: true
#| warning: false
#| label: chicks-plots
#| layout-ncol: 2

tar_load(plot_groups_counts)

plot_groups_counts

```

Body mass:

```{r}
#| echo: true
#| eval: true
#| warning: false
#| label: penguins-plots
#| layout-ncol: 2

tar_load(plot_groups_penguins)

plot_groups_penguins

```

## Next Steps

There is a lot more we can do with a `{targets}` workflow! Check out the Resources page of the workshop for more.
