---
title: "Summary Report"
---

```{r}
#| include: false
targets::tar_source('R')
```

## Data Summary

For this project, we are using three datasets. The first dataset includes Adelie adult and chick counts across islands and years.

```{r}
#| echo: true
#| eval: true
#| warning: false
#| label: counts-summary
tar_load(prepared_counts)
datasummary_skim(data = prepared_counts %>% select(c(island, adults, chicks)))
```


----


The second dataset describes the monthly weather conditions from Palmer Station, Antarctica

```{r}
#| echo: true
#| eval: true
#| warning: false
#| label: weather-summary
tar_load(weather) 
datasummary_skim(data = weather %>% clean_names())
```


---


The final dataset is a widely accessible dataset through the `palmerpenguins` package and includes many variables concerning penguin body condition.

```{r}
#| echo: true
#| eval: true
#| warning: false
#| label: penguins-summary
tar_load(prepared_penguins)
datasummary_skim(data = prepared_penguins |>
                   select(-c(month, date, comments, clutch_completion, species, study_name)))
```

## Modelling

We had two groups of models. The first was looking at how temperature relates to chick counts on different islands.

```{r}
#| echo: true
#| eval: true
#| label: counts-models
tar_load(model_tables)

model_tables
```

------------------------------------------------------------------------

The second was looking at how precipitation affects body mass of Adelie penguins.

```{r}
#| echo: true
#| eval: true
#| label: penguins-models
tar_load(model_penguins)
tar_load(keys_penguins)

setNames(model_penguins, keys_penguins) |>
  modelsummary()

```

## Plots

We can visualize these models. Chick counts:

```{r}
#| echo: true
#| eval: true
#| warning: false
#| label: counts-plots
#| layout-ncol: 2
tar_load(fig_counts)

fig_counts
```

Body mass:

```{r}
#| echo: true
#| eval: true
#| warning: false
#| label: penguins-plots
#| layout-ncol: 2
tar_load(fig_penguins)

fig_penguins
```

## Next Steps

There is a lot more we can do with a `{targets}` workflow! Check out the Resources page of the workshop for more.
