# Extending targets

## Files

{targets} can be used to track external files for changes. This includes input data files but also outputs like saved plots or tables. To signal to {targets} that these target represents an external file to track, use the argument 'format' set to 'file'.

`_targets.R`

``` r
# ...

c(
  tar_target(
    path_file,
    'path/to/some-file.csv',
    format = 'file'
  ),
  tar_target(
    read_file,
    read.csv(path_file)
  )
)
```

```{r}
#| echo: false
#| message: false
#| results: "asis"
library(targets)
tar_dir({
tar_script({
  library(targets)
  tempfile('path/to/some-file.csv')
  tar_option_set()
  c(
    tar_target(
        path_file,
        'path/to/some-file.csv',
        format = 'file'
  ),
  tar_target(
    read_file,
    read.csv(path_file)
  ))
})
cat(
  '```{mermaid}', 
  targets::tar_mermaid(reporter = 'silent', label = 'description'), 
  '```', 
  sep = '\n'
)
})
```

Alternatively, we can use the [`tar_file_read()`])(https://docs.ropensci.org/tarchetypes/reference/tar_file_read.html) function from the 
[{tarchetypes}](https://docs.ropensci.org/tarchetypes) package which is our first example of a 
["target factory"](https://books.ropensci.org/targets/packages.html#target-factories). Target factories are functions that produce multiple targets, with a minimal input. They can be helpful for simplifying our pipelines, generating complex sets of pipelines from standard outputs. 

The `tar_file_read` function simplifies tracking the path to the input file, and reading the input file with a custom read function.
Note how the output network of targets looks the same!

`_targets.R`

``` r
# ...

c(
  tar_file_read(
  file, 
  'path/to/some-file.csv',
  read_csv(file = !!.x)
)
```

```{r}
#| echo: false
#| message: false
#| results: "asis"
library(targets)
tar_dir({
tar_script({
  library(targets)
  library(tarchetypes)
  tempfile('path/to/some-file.csv')
  tar_option_set()
    c(
  tar_file_read(
  file, 
  'path/to/some-file.csv',
  read_csv(file = !!.x)
))
})
cat(
  '```{mermaid}', 
  targets::tar_mermaid(reporter = 'silent', label = 'description'), 
  '```', 
  sep = '\n'
)
})
```


## Targetopia

Let's look at other examples of target factories in the ["targetopia"](https://wlandau.github.io/targetopia/) group of packages:

## Iterating

Like we mentioned in the functions resources, there are plenty of options in R for iterating including:

-   the `apply` family
-   {purrr}
-   {dplyr} with `group_by` and `mutate`
-   {data.table}'s by

{targets} offers a new approach that integrates into our pipeline seamlessly and extends our functions to run over groups of rows in a data.frame. There are two steps:

1.  Use the {tarchetypes} function `tar_group_by()` to define the variables to group the data.frame on.
2.  Use "dynamic branching" with the `tar_target()` argument `pattern`.

For example:

`_targets.R`

``` r
#...
c(
    # Group the mtcars data.frame by the values in the column "cyl"
    tar_group_by(
        group_counts,
        mtcars,
        cyl
    ),

    # Averages by group
    tar_target(
        mean_mpg,
        mean(mtcars$mpg),
        pattern = map(mtcars)
    ),

    # Summarize all the cars
    tar_target(
        summarize_cars,
        summarize(group_counts)
    )
)
```

We pass the data.frame to the `command` argument, and the following arguments are the column names to group on (in this case `cyl`). Then downstream targets that want to iterate over the groups of rows use the argument `pattern` with the function `map()`. The target corresponding to the grouped data.frame is passed to `map()`.

If you want to use the full dataset, ungrouped, again downstream simply refer to the target without the `pattern` argument and {targets} will automatically combine the data.frame again.

Another approach that Alec likes to use with {data.table} is:

`_targets.R`

``` r
# ...

# Variables
# Split by: within which column or set of columns (eg. c(id, yr))
#  do we want to split our analysis?
split_by <- c('id', 'species')

# Targets
c(
    tar_target(
        split_data,
        data[, tar_group := .GRP, by = split_by],
        iteration = 'group'
    ),
    tar_target(
        split_key,
        unique(locs_prep[, .SD, .SDcols = c(split_by, 'tar_group')])
    )

)
```

Read more:

-   `tar_group_by()`: <https://docs.ropensci.org/tarchetypes/reference/tar_group_by.html>
-   `tar_group_count()`: <https://docs.ropensci.org/tarchetypes/reference/tar_group_count.html>
-   `tar_group()`: <https://docs.ropensci.org/targets/reference/tar_group.html>

These are example of "dynamic branching", but also see "static branching" functions:

-   `tar_map`: <https://docs.ropensci.org/tarchetypes/reference/tar_map.html>
-   `tar_rep`: <https://docs.ropensci.org/tarchetypes/reference/tar_rep.html>

### `iteration = 'list'`

The `iteration` argument for `tar_target()` is used to change how {targets} splits and combines branches. This is is required when you want to return objects like plots, models or matrices that aren't obviously combined.

For example:

`_targets.R`

``` r
#...
c(
    # Group the mtcars data.frame by the values in the column "cyl"
    tar_group_by(
        group_counts,
        mtcars,
        cyl
    ),

    # Averages by group
    tar_target(
        plot_cars,
        ggplot(mtcars) + geom_histogram(mpg),
        pattern = map(mtcars),
        iteration = 'list'
    ),

    # Matrix of correlations between vars
    tar_target(
        correlation_metrics,
        cor(mtcars),
        pattern = map(mtcars),
        iteration = 'list'
    )
)
```

See more details for argument `iteration` in `?tar_target`: <https://docs.ropensci.org/targets/reference/tar_target.html>


## Bonus

### tar_option_set

Look into the arguments provided by `tar_option_set()`. This is link to the full reference page: <https://docs.ropensci.org/targets/reference/tar_option_set.html>

-   `format` argument
    -   for `data.table` objects you can use {qs} and format qs to retain data.table clas
-   `error` argument to define what {targets} should do when it hits an error
-   `workspace_on_error` argument to optionally save a workspace file for each target that throws an error
-   `cue` argument

If you are already done all the previous exercises and have extra time, or on your own after the workshop, try this bonus exercise:

-   write a function that processes the ice data
-   look at the relationship between adult and chick counts, and the ice data and weather data. How might these two be influencing adult and chick counts?
